Fast approximate Bayesian inference for the Naomi model

### 2023-06-21 src/docs_21-06-23-mlgh/21-06-23-mlgh.Rmd
Finish slides #40

```{r, echo=FALSE, fig.cap="Naomi is a district-level model of HIV indicators, like prevalence, treatment coverage, and incidence.", out.width = '90%'}
knitr::include_graphics("depends/naomi_results.png")
```

@@

```{r, echo=FALSE, fig.cap="Estimate generation via a web interface promotes data ownership, data use, and data quality. From \\texttt{https://naomi.unaids.org/.}", out.width = '70%'}
knitr::include_graphics("naomi_user.png")
```

# Better estimates by integration information from many sources

@@

# Put together, it's a challenging Bayesian inference problem

@@

If you input 24 length $\btheta$ then it'll return a 467 length mean vector $\hat \x(\btheta)$ and $467 \times 467$ length covariance matrix $\hat{\mathbf{H}} (\btheta)$.
Mean calculated using gradient based optimisation.
Gradients, and Hessian, obtained using automatic differentiation.

@@

@@

```{r, echo=FALSE, message=FALSE, fig.cap=".", out.width = '90%'}
knitr::include_graphics("depends/tv-plot.png")
```

@@

```{r, echo=FALSE, message=FALSE, fig.cap=".", out.width = '90%'}
knitr::include_graphics("depends/reduced-rank-plot.png")
```

@@

1. Further directions for this research $\color{lolit}{\text{e.g. suggestions for short masters or PhD projects}}$  
2. Impactful academic or industry jobs using Bayesian statistics $\color{lolit}{\text{to begin around the end of this year when I graduate (hopefully!)}}$

@@

>>>>

```{r, echo=FALSE, fig.cap="Naomi is a age-sex-district model of HIV indicators, like prevalence, treatment coverage, and incidence, for countries in sub-Saharan Africa.", out.width = '90%'}
knitr::include_graphics("depends/naomi_results.png")
```

@@

```{r, echo=FALSE, fig.cap="Estimates are generated yearly via a web interface. This promotes data ownership, data use, and data quality. From \\texttt{https://naomi.unaids.org/.}", out.width = '70%'}
knitr::include_graphics("naomi_user.png")
```

# Integration of information from many sources

@@

# A challenging Bayesian inference problem

@@

\lolit{
If you input 24 length $\btheta$ then it'll return a 467 length mean vector $\hat \x(\btheta)$ and $467 \times 467$ length covariance matrix $\hat{\mathbf{H}} (\btheta)$.
Mean calculated using gradient based optimisation.
Gradients, and Hessian, obtained using automatic differentiation.
}

Optimise the resulting Laplace approximation

$$
\hat{\btheta}_{\texttt{LA}} = \argmax_{\btheta} \tilde p_{\texttt{LA}}(\btheta, \y) = \argmax_{\btheta} \frac{p(\y, \x, \btheta)}{\tilde p_{\texttt{G}}(\x \, | \, \btheta, \y)} \Big\rvert_{\x = \hat{\x}(\btheta)}
$$

@@

$$
p(\y) \approx \int_{\btheta} \tilde p_{\texttt{LA}}(\btheta, \y) \text{d}\btheta \approx \sum_{\z \in \mathcal{Q}} p_{\texttt{LA}}(\z, \y) \omega(\z)
$$
where $\z \in \mathcal{Q}$ are a set of nodes and $\omega: \mathcal{Q} \to \mathbb{R}$ is a weighting function.

@@

```{r, echo=FALSE, message=FALSE, fig.cap="Including 8 dimensions you can explain close to 90\\% of the total variation.", out.width = '90%'}
knitr::include_graphics("depends/tv-plot.png")
```

@@

```{r, echo=FALSE, message=FALSE, fig.cap="If you reconstruct the Hessian with just those 8 dimensions, it looks pretty similar.", out.width = '90%'}
knitr::include_graphics("depends/reduced-rank-plot.png")
```

@@

1. You have suggestions to improve the work done so far!
2. Further directions for this research $\color{lolit}{\text{e.g. suggestions for short masters or PhD projects}}$  
3. Impactful academic or industry jobs using Bayesian statistics $\color{lolit}{\text{to begin around the end of this year when I graduate (hopefully!)}}$

@@

```{r, echo=FALSE, fig.cap="Custom version of Laplace marginals implemented using \\texttt{TMB}. Speed-up possible using Simon Wood's method? For the Epilepsy example from Rue (2009), see \\texttt{athowes/elgm-inf/src/epil}.", out.width = '60%'}
knitr::include_graphics("laplace.png")
```
